\section{Literature Review}
\label{sec:related}
\subsection{Stress-buffering Function of Positive Events}
%3.对自杀，孤独感，压力的调节作用
Positive events have been verified as protective factors against daily stress~\citep{Ong2006Psychological,Bono2013Building}, loneliness~\citep{Chang2015Loneliness}, suicide~\citep{Evan2014Social} and depression~\citep{Santos2013The}.
By exploring naturally occurring daily stressors, \citep{Ong2006Psychological} found that over time,
the experience of positive emotions assisted high-resilient individuals in recovering effectively from daily stress.
Through a three-week longitudinal study, \citep{Bono2013Building} examined the correlation between employee stress and health and positive life events.
They concluded that naturally occurring positive events were correlated with decreased stress and improved health.
\citep{Chang2015Loneliness} investigated the protective effect of positive events in a sample of 327 adults and found that the positive association between loneliness and psychological maladjustment was weaker for those who experienced a large number of positive life events, as opposed to those who experienced a small number of positive life events.
This finding agrees with the conclusion made by \citep{Evan2014Social} that positive events act as protective factors against suicide individually and synergistically when they co-occurred,
by buffering the link between important individual differences in risk variables and maladjustment.
In the survey concluded by \citep{Santos2013The},
strategies of positive psychology were also identified as potential tools for the prophylaxis and treatment of depression, helping to reduce symptoms and prevent relapses.

%2.积极事件作用的两种方式
The protective effect of positive events was hypothesized to operate in both direct (i.e., the more positive events people experienced, the less stress they perceived)
and indirect ways by '\emph{buffering}' the effect of stressors ~\citep{Cohen2010Positive,Shahar2002Positive},
with respect to physiological, psychological, and social coping resources ~\citep{Cohen1984Positive, Needles1990Positive}.
%1.积极事件保护的三个方面：积极重新评价，针对问题，创建新积极事件
\citep{Folkman2010Stress} identified three classes of coping mechanisms that were associated with positive emotions during chronic stress: positive reappraisal, problem-focused coping, and the creation of positive events.
%4. 青少年积极事件：对身心调节作用
Due to their immature inner status and lack of experience,
adolescents exhibit more sensitivity to stressors
(i.e., exams, heavy homework load, isolation by classmates, family transitions),
and live with frequent, long-term stress~\citep{older}.
In this situation, positive events could help reinforce adolescents' sense of well-being~\citep{Coolidge2009A} and restore the capacity to handle stress~\citep{Doyle2003Positive}.
Positive events have also been linked to medical benefits, such as improved mood, serum cortisol levels, and lower levels of inflammation and hypercoagulability~\citep{Jain2010Effects,Caputo1998Influence}.
The present study will be based on the consensus conclusions from the above studies.

To assess the stress-buffering effect of positive events, scholars conducted various studies based on self-support methods.
For example, \citep{Kanner1981Comparison} developed the Hassles and Uplifts Scale and concluded that the assessment of daily hassles and uplifts might be a better approach to the prediction of adaptational outcomes than the usual life-events approach.
To measure the negative interpretations of positive social events,
\citep{Alden2008Social} proposed the Interpretation of Positive Events Scale and analyzed the relationship between social interaction anxiety and the tendency to interpret positive social events in a threat-maintaining manner.
\citep{Mcmillen1998The} proposed the Perceived Benefit Scales as new measures of self-reported positive life changes after traumatic stressors, including lifestyle changes, material gain, increases in self-efficacy, family closeness, community closeness, faith in people, compassion, and spirituality.
Specific to college students,
\citep{Jun2008Influence} administered the Adolescent Self-Rating Life Events Checklist to 282 college students and
found training in positive coping styles was of great benefit to improve the mental health of students.
The above explorations are based on self-report investigations, 
which are difficult to exclude the interference from external factors (i.e., social pressure and pressure from measurement scenarios). 
Moreover, due to the lack of personnel and effective scientific methods, 
most scholars have relied on a limited number of measurements; 
thus, continuous measurements of the stress-buffering process were difficult to carry out.

\subsection{Measures and Stress Analysis from Social Networks}
As billions of adolescents are recording their lives through social networks (e.g., microblogs, Twitter and Facebook),
researchers have explored applying psychological theories to social network-based data mining techniques
to better understand user' psychological statuses from the self-expressed public data source.
Multiple content and user behavioral measures have been proven effective in user mental health analysis,
including time series curve analysis of stress~\citep{Li2015When,Li2015Using}, topic words~\citep{XueUbicomp13}, abnormal posting time~\citep{Xue2014Detecting},
online shopping behaviors~\citep{DBLP:conf/apweb/Zhao0XLF16},
human mobility features~\citep{DBLP:conf/dasfaa/JinXLF16}, comment/response actions~\citep{Liang2015Teenagers}
and high-dimensional multimedia features~\citep{Lin2014User}.
For example,
\citep{XueUbicomp13, Xue2014Detecting} proposed detecting adolescent stress from a single post utilizing machine learning methods
by extracting topic words indicating stress, abnormal posting time, and interactions with friends.
\citep{Lin2014User} constructed a deep neural network to combine the high-dimensional pictorial information into stress detection.
Based on the stress detection results,
\citep{Li2015Predicting,Li2015Using,Li2015When} adopted a series of multivariate time series prediction techniques (i.e., candlestick charts, fuzzy candlestick lines and the seasonal Autoregressive Integrated Moving Average model) to predict future stress trends.
Taking linguistic information into consideration,
\citep{Li2017Exploring} employed a nonlinear autoregressive with external input neural network to predict a teenager's future stress level
by referring to the impact of co-experienced stressor events of similar companions.
\citep{Li2017Analyzing} proposed detecting stressor events from microblog content and analyzing stressful intervals based on the posting rate.
All of the above studies focused on the discussion of stress detection in social networks.
This paper starts from a completely new perspective and focuses on the stress-buffering effect of positive events in adolescents' stress coping processes.
Thus, we extend the study from how to find stress to the next more meaningful stage: how to cope with stress.

\subsection{Correlation Analysis Models for Multivariate Time Series}
Basic correlation analysis models on time series focusing on univariate data have been well studied.
As the most widely adopted model,
the Pearson correlation coefficient~\citep{Cohen1988Statistical} measures the linear correlation between two variables $X$ and $Y$.
One inevitable defect of the Pearson correlation coefficient is its sensitivity to outliers.
To overcome such drawbacks,
Spearman's rank correlation coefficient~\citep{C1987The} and the Kendall rank correlation coefficient~\citep{Mcleod2011Kendall}
were proposed based on the Pearson correlation coefficient.
While the Pearson correlation coefficient estimates linear relationships,
Spearman's correlation coefficient estimates monotonic relationships (regardless of linearity),
and are calculated as the Pearson correlation coefficient between the rank values of two variables.
The Kendall rank correlation coefficient mainly assesses the similarity of the orderings of the data when ranked by each of the quantities.
The above correlation metrics are primarily used to estimate the relationship between single-dimensional variables,
and cannot be adopted directly in social network-based scenarios.

For multivariate time series analysis,
two-sample models are widely adopted.
Such models are built to check whether two samples come from the same underlying distribution,
which is assumed to be unknown.
Correspondingly,
various kernel-based~\citep{Sch2006A} and distance-based models \citep{Schilling1986Multivariate} have been proposed.
\citep{Sch2006A} proposed to transform the distance between two variables and nearest neighbors
into a reproducing kernel Hilbert pace and to solve the problem using the maximum mean discrepancy.
\citep{Schilling1986Multivariate} adopted an $r$-nearest-neighbor-based model to partition two sets of event-driven time series data.
The global proportion of right divided neighbors was calculated to estimate whether there existed
a statistically significant difference between the two sets.
This paper adopted an $r$-nearest-neighbor-based two-sample model in our problem
to measure the distance and correlation between two multidimensional variables
depicting the stress-buffering patterns of positive events.
