\section{Literature Review}
\subsection{Stress-buffering Function of Positive Events}
%3.对自杀，孤独感，压力的调节作用
Positive events have been verified as protective factors against daily stress~\citep{Ong2006Psychological,Bono2013Building}, loneliness~\citep{Chang2015Loneliness}, suicide~\citep{Evan2014Social} and depression~\citep{Santos2013The}.
Through exploring naturally occurring daily stressors, \citep{Ong2006Psychological} found that over time,
the experience of positive emotions functions to assist high-resilient individuals to recover effectively from daily stress.
Through a three-week longitudinal study, \citep{Bono2013Building} examined the correlation between employee stress and health and positive life events, and concluded that naturally occurring positive events are correlated with decreased stress and improved health.
\citep{Chang2015Loneliness} investigated the protective effect of positive events in a sample of 327 adults, and found that the positive association between loneliness and psychological maladjustment was found to be weaker for those who experienced a high number of positive life events, as opposed to those who experienced a low number of positive life events.
This is assistant with the conclusion made by \citep{Evan2014Social} that positive events acted as protective factors against suicide individually and synergistically when they co-occurred,
by buffering the link between important individual differences risk variables and maladjustment.
In the survey made by \citep{Santos2013The},
strategies of positive psychology were also checked as potentially tools for the prophylaxis and treatment of depression, helping to reduce symptoms and for prevention of relapses.

%2.积极事件作用的两种方式
The protective effect of positive events was hypothesized to operate in both directly (i.e., the more positive events people experienced, the less stress they perceived)
and indirectly ways by \emph{'buffering'} the effect of stressors ~\citep{Cohen2010Positive,Shahar2002Positive},
with respect to physiological, psychological, and social coping resources ~\citep{Cohen1984Positive, Needles1990Positive}.
%1.积极事件保护的三个方面：积极重新评价，针对问题，创建新积极事件
\citep{Folkman2010Stress} identified three classes of coping mechanisms that were associated with positive emotion during chronic stress: positive reappraisal, problem-focused coping, and the creation of positive events.
%4. 青少年积极事件：对身心调节作用
Due to the immature inner status and lack of experience,
adolescents exhibit more sensitive to stressors
(i.e., exams, heavy homework, isolated by classmates, family transitions),
living with frequent, long-term stress~\citep{older}.
In this situation,
positive events could help reinforce adolescents' sense of well-being~\citep{Coolidge2009A},
restore the capacity for dealing with stress~\citep{Doyle2003Positive},
and also have been linked to medical benefits, such as improving mood, serum cortisol levels, and lower levels of inflammation and hyper coagulability \citep{Jain2010Effects,Caputo1998Influence}.
The present study will be based on the consensus conclusions from the above studies.

To assess the stress-buffering effect of positive events,
scholars conducted many studies based on self-support methods.
For example,
\citep{Kanner1981Comparison} conducted Hassles \& Uplifts Scales,
and concluded that the assessment of daily hassles and uplifts might be a better approach to the prediction of adaptational outcomes than the usual life events approach.
To measure negative interpretations of positive social events,
\citep{Alden2008Social} proposed the Interpretation of Positive Events Scale, and analyzed the relationship between social interaction anxiety and the tendency to interpret positive social events in a threat-maintaining manner.
\citep{Mcmillen1998The} proposed the Perceived Benefit Scales as the new measures of self-reported positive life changes after traumatic stressors, including lifestyle changes, material gain, increases in self efficacy, family closeness, community closeness, faith in people, compassion, and spirituality.
Specific for college students,
\citep{Jun2008Influence} investigated in 282 college students using the Adolescent Self-Rating Life Events Checklist, and found that the training of positive coping style was of great benefit to improve the mental health of students.
The above explorations based on self-report investigations
were difficult to exclude interference from external factors (i.e., social appreciation, pressure from measurement scenarios).
Meanwhile, due to the lack of manpower and effective scientific methods,
most scholars relied on a limited number of measurements,
thus continuous measurements of stress-buffering process were difficult to carry out.

\subsection{Measures and Stress Analysis from Social Networks}
As billions of adolescents are recording their life through social networks (e.g., micro-blog, Twitter, Facebook),
researchers explored to apply psychological theories into social network based data mining techniques,
thus to better understand user' psychological status from the self-expressed public data source.
Multiple content and user behavioral measures have been proven effective in user mental health analysis,
including time series curve analysis of stress~\citep{Li2015When,Li2015Using}, topic words~\citep{XueUbicomp13}, abnormal posting time~\citep{Xue2014Detecting},
online shopping behaviors~\citep{DBLP:conf/apweb/Zhao0XLF16},
human mobility features~\citep{DBLP:conf/dasfaa/JinXLF16}, comment/response actions~\citep{Liang2015Teenagers} 
and high dimensional multimedia features~\citep{Lin2014User}.
For example,
\citep{XueUbicomp13, Xue2014Detecting} proposed to detect adolescent stress from single post utilizing machine learning methods by extracting stressful topic words, abnormal posting time, and interactions with friends.
\citep{Lin2014User} constructed a deep neural network to combine the high-dimensional picture semantic information into stress detecting.
Based on the stress detecting result,
\citep{Li2015Predicting}\cite{Li2015Using}\cite{Li2015When} adopted a series of multi-variant time series prediction techniques (i.e., Candlestick Charts, fuzzy Candlestick line, Seasonal Autoregressive Integrated Moving Average model) to predict future stress trend.
Taking the linguistic information into consideration,
\citep{Li2017Exploring} employed a Nonlinear autoregressive with External Input Neural Network to predict a teen's future stress level referred to the impact of co-experiencing stressor events of similar companions.
\citep{Li2017Analyzing} proposed to detect stressor events from microblog content
and analyze stressful intervals based on posting rate.
All above studies focused on the discussion of stress detection on social networks.
This paper starts from a completely new perspective,
and focuses on the stress-buffering effect of positive events in adolescents' stress coping process.
Thus we push forward the study from how to find stress to the next more meaningful stage: how to cope with stress.

\subsection{Correlation Analysis Models for Multivariate Time Series}
Basic correlation analysis models on time series focused on univariate data have been well studied.
As the most widely adopted model,
the Pearson correlation analysis \cite{Cohen1988Statistical} measures the linear correlation between two variables $X$ and $Y$.
One inevitable defect of Pearson correlation is its sensitivity to outlier values.
To overcome such drawback,
Spearman Rank correlation \cite{C1987The}
and Kendall Rank correlation \cite{Mcleod2011Kendall}
were proposed based on Pearson correlation.
While Pearson correlation estimates linear relationships,
Spearman correlation estimates monotonic relationships (whether linear or not),
and are calculated as the Pearson correlation between the rank values of two variables.
The Kendall Rank correlation mainly assesses the similarity of the orderings of the data when ranked by each of the quantities.
The above correlation models are usually used to estimate relationship between single-dimensional variables,
and cannot be adopted directly in social network based scenario.

For multivariate time series analysis,
two-sample based models were widely adopted.
Such kind of models were deduced to check whether two samples come from the same underlying distribution,
which was assumed to be statistically unknown.
Correspondingly,
various kernel \citep{Sch2006A} and distance-based models \citep{Schilling1986Multivariate} were proposed.
\citep{Sch2006A} proposed to transform the distance between two variables and nearest neighbors into a reproducing kernel hilbert pace, and solve the problem using Maximum Mean Discrepancy.
\citep{Schilling1986Multivariate} adopted the $r$-nearest neighbor based model to partition two set of event driven time series data.
The global proportion of the right divided neighbors were calculated to estimate whether there existed statistically difference between the two sets.
This paper adopted the $r$-nearest neighbor based two-sample model in our problem,
thus to measure the distance and correlation between two multi-dimension variables depict
the stress-buffering patterns of positive events.
