\section{Discussion}
\label{sec:conclude}
The main contribution of the present study lies in the following three aspects.
%第一，验证和拓展了以往研究的结果。不只是在主观感受上，还表现在个体的行为上
First, we validated and expanded the theoretical results of previous studies.
The characteristics of stress-buffering were not only manifested in self-reported subjective feelings,
but also in behavioral level in social networks.
%理论的创新：检验了积极事件的发生与压力状态下的青少年发布微博行为、微博内容及压力变化之间的潜在关联关系，并验证了积极事件的压力缓解作用分别体现在减缓前期的压力升高和加速后期的压力降低两方面。（研究结果）
We examined the potential relationship between the occurrence of positive events and the posting behaviors,
microblog contents and stress change mode on stressed adolescents,
and verified that
positive events buffered monotonous stress changes at both the early and late stages.
%第二，本文实现了方法上的创新。本研究搭建了一个完整的技术框架，实现了1）基于微博数据自动抽取积极事件及用户行为变量，2）基于网络行为，量化当前积极事件缓解下的微博行为模式，3）建构模型实时监测青少年的压力缓解进程。
Second, this study implemented the innovation of methods.
Through building a complete technical framework,
we realized
1) automatic extraction of positive events, as well as users' behavior and content measures from microblogs,
and 2) quantification of relationships between stress-buffering of positive events and microblogging measures.
%第三，重大现实意义：一方面实现了基于微博公开数据源，对青少年的压力缓解进程做出及时、连续监测，可用于评估青少年个体的抗压性；另一方面，可对学校和家长何时安排何种积极事件以缓解青少年压力提供辅助建议。
Third, this article showed practical significance.
It realized timely and continuous monitoring of the stress-buffering process
of adolescents based on public social network data sources,
which could be used to assess the stress resistance of adolescents;
on the other hand, it could provide supplementary advice to schools and parents about
'when to arrange positive events to ease stress of adolescents'.

%2
There were three groups of results in this work.
In study 1, the scheduled school events with exact time intervals and the microblogs posted by a group of 500 students were collected and statistically analyzed.
Results showed that when positive events were scheduled neighboring stressful events,
students exhibited less stress intensity and shorter stressful time intervals from their microblogs.
The study also found that most students talked less about the upcoming or just-finished exams when positive events happened nearby,
with lower frequency and lower ratio.
The results substantiated previous studies reporting the protective effect of positive events on adolescents~\citep{Cohen2010Positive,Shahar2002Positive} using laboratory methods.
Based on this, this article carried out more in-depth follow-up studies.

The second groups of results were presented in study 2,
examining stress-buffering pattern of positive events through microblog content and behavioral measures.
As basis, a complete solution was provided for automatically detecting positive events based on microblog semantics,
which were totally different from traditional questionnaire methods,
enabling timely, fraud-proof and continuous detection.
In order to eliminate the possible errors in positive event detection and avoid false overlays,
we first used four scheduled positive events to examine significant stress-buffering effects.
Results showed the event 'holiday' exhibited the highest proportion of significant stress-buffering.
However, this conclusion was questionable because the frequency of the above four events was different and might affect the experimental results.
Next, the stress-buffering effect of automatically extracted positive events were tested based on three groups of stress-buffering measures.
The most intensive stress-buffering effects were shown in 'school life' and 'peer relationship' dimensions.
\emph{Posting behaviors} exhibited most significant correlations among three groups of measures.
This resonated with the study \cite{BLACHNIO2016664,Disclosure} suggesting that users who
tended to share important news on Facebook had a higher level of stress.

This article proposed a novel perspective to better understand the process of stress-buffering.
Since more complex situations were simplified in the present exploration,
the goals were still salient for stress-buffering researches from social networks.

\section{Limitations and future work}

This study has a number of limitations.
% 1) study 1 的数据观察忽略了个人事件
First, it used the microblog data set collected from social networks of high school students,
and chose the scheduled school events as the ground truth in the pilot study.
This could be seen as a relative fuzzy verification method,
because individual events (i.e., 'lost love', or 'received a birthday present') might also conduct additional impact.
Therefore, the data observation in the pilot study were not 100\% rigorous and needed further verification.
A improvement might be conducted by inviting participants to complete related scales (e.g., positive and stressor scales),
thus to label part of the data set,
and achieve a balance between data volume and accuracy.

% 3) 未考虑叠加影响
Second,
this study treated positive events as independent existence and studied the effect of each event separately.
This ignored the additive and collective effects of multiple positive events which might happened at the same time.
Thus, our future research might investigate the overlap effects of multiple positive events,
as well as the frequent co-appearing patterns of different types of positive events,
thus to provide more accurate stress-buffering guidance for individual adolescents.
%: 1) personality, 2) social support

Based on current research implications,
more factors could help analyze stress-buffering patterns among adolescents more comprehensively in future research.
One factor is how personality ~\citep{personality1,personality2} impacts the stress-buffing effect of positive events,
which could be captured from the social media contents.
Another key factor is the role the social support~\citep{socialSupport1, socialSupport2} in social networks plays.
This factor leaves clues in the messages under each post,
and the behaviors (i.e., retweet, the like numbers) of friends.
For examples, ~\citep{socialSupport1} showed that the number of Facebook friends was associated with stronger perceptions of social support,
which in turn correlated with reduced stress and greater well-being.
The corresponding experimental design, and the online-offline complementary verification will be the key challenges in the future work.
%后续结合线上线下会更准确。但是大数据量下难以执行，有效的自动标记方法需要更多的探索。

%\section*{References}
