\documentclass[5p,times,numbers,authoryear]{elsarticle}

\usepackage{ctex}
\usepackage{lineno}%,hyperref}
\usepackage[colorlinks,citecolor=blue]{hyperref}

\usepackage{graphics}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{subfigure}
\usepackage{helvet}
\usepackage{courier}
\usepackage{diagbox}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage[justification=centering]{caption}
\usepackage[linesnumbered,ruled,vlined,commentsnumbered]{algorithm2e}
\usepackage{color}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{float}
\usepackage{bm}
\usepackage[normalem]{ulem} % use normalem to protect \emph
\newcommand\hl{\bgroup\markoverwith
  {\textcolor{yellow}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}

\usepackage{hyperref}
\usepackage{breakurl}

\newtheorem{definition}{Definition}
\def\boxend{\hspace*{\fill} $\Box$}
\newcommand{\comment}[1]{}
\renewcommand{\multirowsetup}{\centering}

\journal{Journal of \LaTeX\ Templates}

\usepackage{appendix}

\begin{document}

\begin{frontmatter}

\title{Stress-Buffering Pattern of Positive Events on Adolescents: \\
An Exploratory Study based on Social Networks}

%\author[mymainaddress]{Qi Li}

%\ead{liqi2018@bnu.edu.cn}
%
%
%\author[my3address]{Liang Zhao}
%\ead{zhaoliang0415@xjtu.edu.cn}

%\author[my2address]{Yuanyuan Xue}
%\ead{xue-yy12@mails.tsinghua.edu.cn}
%
%\author[my2address]{Ling Feng\corref{mycorrespondingauthor}}
%\cortext[mycorrespondingauthor]{Dept. of Computer Science and Technology, Centre for Computational Mental Healthcare Research,
%Tsinghua University, Beijing, China.}
%\ead{fengling@tsinghua.edu.cn}
%
%\address[mymainaddress]{Faculty of Psychology, Beijing Normal University, Beijing, China.}
%\address[my2address]{Dept. of Computer Science and Technology, Tsinghua University, Beijing, China.}
%\address[my3address]{Institute of Social Psychology, Xi'an Jiaotong University, Xi'an, China.}

\begin{abstract}
Stress is viewed as the leading cause of public mental health issues. 
Positive events, however, could act as a buffer against stress. 
%1.主观自陈 %2.静态视觉
Since the stress-buffering effect of positive events was examined mainly through subjective self-reporting, 
continuous tracking research on individual behavioral levels still remains to be explored. 
In this study, 
We collected microblogs (n=29,232) from a high school student group (n=500) 
to examine the relationship 
between positive events and stress-buffering effect through both the microblog content and behavioral characteristics. 
%result1
Through a pilot study, 
we found that the stress-buffering pattern of school scheduled positive events (n=259) 
was manifested in the reduction in stress intensity (78.13\% reduction in average stress, 95.58\%  reduction in cumulative stress), 
the shorter duration of stress intervals (23.30\%),
and talking less about academic words (84.65\% reduction in frequency, 89.53\% reduction in ratio) on micro-blog. 
The hypothetical tests for stress-buffering pattern and monotonic effect of stress changes were further conducted 
based on automatical extracted positive events from microblogs. 
%result2
The stress-buffering pattern of positive events 
was correlated with posting behavior (xx\%), stress change mode (xx\%) and linguistic expressions (xx\%) on micro-blog. 
Stress from peer relationships and family life exhibited the most obvious buffering patterns. 
%restul3
Positive events buffered monotonous stress changes in both the early (11.88\% reduction) and late stages (5.88\% reduction). 
This study could inform the use of social network to reach and track the mental status transition of adolescents under stress. 
The theoretical and practical implications, limitations of this study and future work were discussed. 
\end{abstract}

\begin{keyword}
stress-buffering, positive events, adolescents, microblogs
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}
Life is always full of ups and downs.
Accumulated stress comes from daily hassles,
major stressful events and environmental stressors could drain inner resources,
leading to psychological maladjustment, such as depression and suicidal behaviours \citep{Nock2008Suicide}.
According to the newest report of American Psychological Association,
91 percent of youngest adults say they have experienced physical or emotional symptom due to stress in the past month compared to 74 percent of adults overall \citep{APA2018}.
More than 30 million Chinese teenagers are suffering from psychological stress,
and nearly 30\% of them have a risk of depression \citep{ChinaTeen2019}.
Stress-induced mental health problems are becoming an important social issue worldwide.
%1.心理压力问题很严重

Studies have found that the occurrence of positive events could conduct exert obvious protective effects on emotional distress, that is, \emph{stress-buffering} ~\citep{Cohen1984Positive, Folkman1997Positive, Needles1990Positive, Folkman2010Stress, Shahar2002Positive}.
As an essential process in human's stress coping system,
stress-buffering helps individuals get out of overwhelmed status ~\citep{Susan1984Stress,Wheeler1988Identification,Cohen2010Positive}.
Thus, accurately assessing the state of stress-buffering is important for judging the mental health trends of overwhelmed individuals.
%2.积极事件可以缓解心理压力。

However, assessing people's stress-buffering status was not a trivial task.
Previous assessments of stress-buffering were mainly conducted through subjective self-reporting \citep{Kanner1981Comparison, Alden2008Social, Mcmillen1998The, Jun2008Influence},
which was influenced by many factors, such as social appreciation and pressure from measurement scenarios.
However, there is a lack of research on the stress-buffering characteristics that individuals actually exhibit at the behavioral level.
At the same time,
previous studies has been based on static perspectives,
focusing on single measurements of positive events and psychological state after events \citep{Chang2015Loneliness, Evan2014Social, Santos2013The},
while the dynamic process of stress-buffering was difficult to track due to the lack of effective scientific methods.
%3.已有方法存在的确定。

%%1.主观自陈
%The assessment of stress-buffering in previous studies was mainly conducted through subjective self-reporting, and was influenced by many factors, such as social appreciation and pressure from measurement scenarios.
%However, there is a lack of research on the stress-buffering characteristics that individuals actually exhibit at the behavioral level.
%%2.静态视觉
%At the same time,
%previous studies has been based on static perspectives,
%focusing on single measurements of events and psychological state after events, while the dynamic process of stress-buffering was difficult to track due to the lack of effective scientific method.

As the social media is becoming deeply woven into our daily life,
an increasing number of natural self-disclosures are taking place,
thus providing a new channel for timely,
content-rich and non-invasive exploration of adolescents' mental health status.
%4.随着社交媒体大数据兴起，为探索用户心理健康状态提供了及时/非侵入的新途径。
Previous studies have shown the feasibility and reliability to sense user's psychological stress and stressor events,
and predict future development of stress through social network \citep{Li2015Predicting, Xue2014Detecting, Lin2014User, Li2017Analyzing}.
%5.前期研究表明，通过社交网络数据，可以检测心理压力，压力源事件，预测未来心理压力趋势等，是可行的，可靠的。
The current study aims to contribute to this growing area of interdisciplinary  research by examining
the potential relationship between positive events and adolescent's microblogging behaviors,
and track the stress-buffering process in a dynamic perspective from microblogs.


\input{literature}
\input{1pilotstudy}
%\input{study2}
\input{2study_2_3}
%\input{3exploration}
\input{discussion}
%\bibliographystyle{elsarticle-num-names}
\bibliographystyle{model4-names}
\bibliography{reference-new}
\input{appendix}

\end{document}

%The mitigation mechanism of positive events has been well studied in the field of traditional psychology \citep{Shahar2002Positive, Folkman1997Positive, Folkman2010Stress}.
%2.3 积极事件的发生可以缓解压力。
%2.2 人们探求缓解心理压力的多种途径
%and function through various ways,
%such as positive event, social support, sense of competence, exercise pattern, sense of purpose, and leisure activities \citep{Wheeler1988Identification,Cohen2010Positive}.
