\documentclass[10pt, journal]{IEEEtran}%,compsoc
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{subfigure}
\usepackage{helvet}
\usepackage{courier}
\usepackage{diagbox}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage[justification=centering]{caption}
\usepackage[linesnumbered,ruled,vlined,commentsnumbered]{algorithm2e}
\usepackage{color}
\usepackage{xcolor}
%\usepackage{multirow}
%\usepackage[table]{xcolor}
\usepackage{colortbl}
\usepackage{float}
\usepackage{bm}
\usepackage[normalem]{ulem} % use normalem to protect \emph
\newcommand\hl{\bgroup\markoverwith
  {\textcolor{yellow}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}

\usepackage{Cite}

\ifCLASSINFOpdf

\else

\fi

\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{hyperref}
\usepackage{breakurl}
\newtheorem{definition}{Definition}
\def\boxend{\hspace*{\fill} $\Box$}
\newcommand{\comment}[1]{}
\renewcommand{\multirowsetup}{\centering}

\begin{document}

\title{Analyzing the Restoring Impact of Uplift Events on Overwhelmed Teenagers via Microblogs}

\author{Qi~Li,~Yuanyuan~Xue,~Liang~Zhao~and~Ling~Feng~\IEEEmembership{Senior~Member,~IEEE}
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem
\hspace{-0.3cm}$^1$Dept. of Computer Science and Technology,
Centre for Computational Mental Healthcare Research, Institute of Data Science,
Tsinghua University, Beijing, China;\protect\\
$^2$Institute of Social Psychology, Xi'an Jiaotong University, Xi'an, China.\protect\\
E-mail: \{liqi13,xue-yy12\}@mails.tsinghua.edu.cn,\{fengling\}@tsinghua.edu.cn,
\{zhaoliang0415\}@xjtu.edu.cn,
}}

\IEEEtitleabstractindextext{
\begin{abstract}
As an important concept in psychological theory,
restoring is an essential process in human's stress coping system.
Timely and efficient restoring of stress could help teenagers get out of overwhelmed status as soon as possible.
Previous research has explored the possibility of detecting teenagers' stress series and
mining the impact of stressor events from social media.
On the contrary, the research on auto-analyzing the restoring ability of uplift events still calls for more exploration,
due to the uncertainty and complexity of various restoring situations.
In this paper,
we give a deep inside into the stress easing function of uplift events on the real data set of 124 high school students.
A two-sample based statistical model is conducted to analyze the stressful behavioral correlations
when uplift events happened to overwhelmed students from multiple perspectives.
Experimental results show that our method could measure the restoring impact of school scheduled uplift events with 69.52\% accuracy, 
and integrating such impact of uplift events helps reduce the stress prediction errors efficiently (with MSE, RMSE, MAPE and MAD reduced by 49.34\%, 28.81\%, 26.80\% and 42.11\%, respectively). 
Our exploration provides guidance for school and parents that which kind of uplift events could help relieve students' overwhelmed stress in both stress prevention and stress early stopping situations.
\end{abstract}

\begin{IEEEkeywords}
uplift event, stressor event, teenagers, microblogs
\end{IEEEkeywords}
}

\maketitle.

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle

\input{Sec-Introduction}
\input{Sec-RelatedWork}
\input{Sec-Observation}
\input{Sec-Problem}
\input{Sec-Interval}
\input{Sec-Impact}
\input{Sec-Experiment}
\input{Sec-Discussion}
%\section*{Acknowledgments}
%here acknowledgments

\bibliographystyle{IEEEtran}
\bibliography{reference-LiQi} %IEEEabrv,sample
\end{document}


