\section{Introduction}
\paragraph{Stress} Life is always full of ups and downs.
The serious mental health problems caused by stress has become hot issues that are widely concerned around the world.
According to APA's newest report in 2018,
America’s youngest adults are most likely of all generations to report poor mental health,
and 91 percent of Gen Zs between ages 18 and 21 say they have experienced physical or emotional symptom due to stress in the past month compared to 74 percent of adults overall \citeauthor{APA2018}.
Accumulated stress comes from daily hassles, major stressful events and environmental stressors could drain people's inner resources,
leading to psychological maladjustment, ranging from depression to suicidal behaviours \citeauthor{Nock2008Suicide}.
Nowadays more than 30 million Chinese teenagers are suffering from psychological stress,
and nearly 30\% have a risk of depression \citeauthor{ChinaTeen2019}.
%1.心理压力问题很严重

\paragraph{Restoring} As an important concept in psychological theory,
restoring is an essential process in human's stress coping system \citeauthor{Susan1984Stress}.
Timely and efficient restoring of stress could help teenagers get out of overwhelmed status.
%2.心理压力和缓解的原理

人们探求缓解心理压力的多种途径。
其中，传统心理学研究表明，积极事件能够缓解心理压力：1）2）3）。
但是具体的缓解模式仍有待探索。

随着社交媒体大数据兴起，为探索用户心理健康状态提供了及时/非侵入的新途径。
前期研究表明，通过社交网络数据，可以检测心理压力，压力源事件，预测未来心理压力趋势等，是可行的，可靠的。
对于积极事件的探索，亟需展开，从而为及时安排心理压力干预，准确预测心理压力的未来发展趋势提供必要信息。

基于社交网络研究积极事件对于心理压力的缓解作用，存在以下一些困难。
1）2）3）

针对上述挑战，本文的主要贡献包括：
1）2）3）


%Previous research has explored the possibility of detecting teenagers' stress series and
%mining the impact of stressor events from social media.
%On the contrary, the research on auto-analyzing the restoring ability of uplift events still calls for more exploration,
%due to the uncertainty and complexity of various restoring situations.
%In this paper,
%we give a deep inside into the stress easing function of uplift events on the real data set of 124 high school students.
%A two-sample based statistical model is conducted to analyze the stressful behavioral correlations
%when uplift events happened to overwhelmed students from multiple perspectives.
%Experimental results show that our method could measure the restoring impact of school scheduled uplift events with 69.52\% accuracy,
%and integrating such impact of uplift events helps reduce the stress prediction errors efficiently (with MSE, RMSE, MAPE and MAD reduced by 49.34\%, 28.81\%, 26.80\% and 42.11\%, respectively).
%Our exploration provides guidance for school and parents that which kind of uplift events could help relieve students' overwhelmed stress in both stress prevention and stress early stopping situations.


\section{Related Work}

\section{Method}

\section{Study1:}
\section{Study2:}
\section{Study3:}

\section{Discussion}

\section{Conclusion}
In this section, ...
\cite{Alden2008Social}
