\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{subfigure}
\usepackage{helvet}
\usepackage{courier}
\usepackage{diagbox}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage[justification=centering]{caption}
\usepackage[linesnumbered,ruled,vlined,commentsnumbered]{algorithm2e}
\usepackage{color}
\usepackage{xcolor}
\usepackage[normalem]{ulem} % use normalem to protect \emph
\newcommand\hl{\bgroup\markoverwith
  {\textcolor{yellow}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}

%\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  %\usepackage[nocompress]{cite}
%\Else
%  % Normal Ieee
\usepackage{Cite}
%\Fi

\ifCLASSINFOpdf

\else

\fi

\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{hyperref}
\usepackage{breakurl}
%\newcommand\tabhead[1]{\small\textbf{#1}}
%\newtheorem{definition}{\bf Definition}
\newtheorem{definition}{Definition}
\def\boxend{\hspace*{\fill} $\Box$}
\newcommand{\comment}[1]{}
\renewcommand{\multirowsetup}{\centering}

\begin{document}

\title{Analyzing and Identifying Teens Stressful Periods and Stressor Events from a Microblog}

\author{Qi~Li,~Yuanyuan~Xue,~Liang~Zhao,~Jia~Jia~and~Ling~Feng~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem Dept. of Computer Science and Technology,
Centre for Computational Mental Healthcare Research, Institute of Data Science,
Tsinghua University, China.\protect\\
E-mail: \{liqi13,xue-yy12,jing-zhao11\}@mails.tsinghua.edu.cn, \{jjia,fengling\}@tsinghua.edu.cn
}}


%\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}

%\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}

\IEEEtitleabstractindextext{%
\begin{abstract}
Increased health problems among adolescents caused by psychological stress have aroused worldwide attention.
Long-standing stress without targeted assistance and guidance
negatively impacts the healthy growth of adolescents, threatening the future development of our society.
So far, research focused on detecting adolescent psychological stress revealed from each individual post on microblogs.
However, beyond stressful moments, identifying teens stressful periods
and stressor events that trigger each stressful period
is more desirable to understand the stress from appearance to essence.
In this paper, we define the problem of identifying teens stressful periods and stressor events from the open social
media microblog.
Starting from a case study of adolescents' posting behaviors during stressful school events,
we build a poisson-based probability model for the
correlation between stressor events and stressful posting behaviors through a series
of posts on Tencent Weibo (referred to as the microblog throughout the paper).
With the model, we discover teen's maximal stressful periods and
further extract details of possible stressor events that cause the stressful periods.
We generalize and present the extracted stressor events
in a hierarchy based on common stress dimensions and event types.
Taking 122 scheduled stressful study-related events in a high school
as the ground truth, we test the approach on 124 students' posts from
January 1, 2012 to February 1, 2015,
and obtain some promising experimental results: (stressful periods: \emph{recall} 0.761, \emph{precision} 0.737, and $F_1$-\emph{measure} 0.734) and
(top-3 stressor events: \emph{recall} 0.763, \emph{precision} 0.756, and $F_1$-\emph{measure} 0.759).
The most prominent stressor events extracted
are in the \emph{self-cognition} domain, followed by the
\emph{school life} domain. This conforms to the adolescent psychological investigation result
that problems in school life usually accompanied with teens inner cognition problems.
Compared with the state-of-art top-1 personal life event detection approach, our stressor event detection method
is 13.72\% higher in \emph{precision}, 19.18\% higher in \emph{recall}, and 16.50\% higher in $F_1$-\emph{measure},
demonstrating the effectiveness of our proposed framework.
\end{abstract}

\begin{IEEEkeywords}
Adolescent, microblog, stressful period, stressor event.
\end{IEEEkeywords}}

\maketitle.

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle
\input{Sec1-Introduction}
\input{Sec2-RelatedWork}
\input{Sec3-CaseStudy}
\input{Sec4-Framework}
\input{Sec5-Performance}
\input{Sec6-Discussion}
\input{Sec7-Conclusion}

\section*{Acknowledgments}

The authors would like to thank anonymous reviewers for the constructive comments and suggestions, enabling the great improvement of the manuscript.
The work is funded by National Natural Science Foundation of China (61373022, 61532015, 71473146).

%  \section*{Acknowledgment}
%\fi
%
%The authors would like to thank...
%\ifCLASSOPTIONcaptionsoff
%  \newpage
%\fi
%
%\begin{thebibliography}{1}
%
%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
%\end{thebibliography}
%
%
%\begin{IEEEbiography}{Michael Shell}
%Biography text here.
%\end{IEEEbiography}
%
%\begin{IEEEbiographynophoto}{John Doe}
%Biography text here.
%\end{IEEEbiographynophoto}
%
%\begin{IEEEbiographynophoto}{Jane Doe}
%Biography text here.
%\end{IEEEbiographynophoto}

%\bibliographystyle{acm-sigchi}
\bibliographystyle{IEEEtran}
\bibliography{reference-LiQi} %IEEEabrv,sample
\end{document}


