%要大改: 1）跟元素相关 2）跟假设相关 3）层层递进
\section{Literature review}
\subsection{Theoretic stress-buffering function of positive life events.}
%1.积极事件保护的三个方面
Positive life events are conceptualized as exerting a protective effect on emotional distress in psychological literature~\citep{Cohen1984Positive, Needles1990Positive}.
Many psychological researchers have focused on the restorative function of positive events with respect to physiological, psychological, and social coping resources.
\citep{Folkman2010Stress} identified three classes of coping mechanisms that are associated with positive emotion during chronic stress: positive reappraisal, problem-focused coping, and the creation of positive events.
The author also considered the possible roles of positive emotions in the stress process, and incorporated positive emotion into a revision of stress and coping theory in the work \citep{Folkman1997Positive}.
They conducted a longitudinal study of the care giving partners of men with AIDS and described coping processes that were associated with positive psychological states in the context of intense distress.

%2.积极事件作用的两种方式
The protective effect of uplift events was hypothesized to operate in both directly (i.e., more positive uplift events people experienced, the less distress they experience) and indirectly ways by 'buffering' \citep{Cohen2010Positive}.
In the direct way,
the more positive uplift events people experienced, the less distress they experience.
While in the indirectly way, positive life events play its role by buffering the effects of negative events on distress.
A pioneer experiment conducted by Reich and Zautra provided enlightening evidence for us \citep{Shahar2002Positive}.
In this experiment, sampled college students who reported initial negative events were encouraged to engage in either two or twelve pleasant activities during one-month, and compared with students in the controlled group experiencing no pleasant activities.
Results indicated that participants in the two experimental groups reported greater quality of life compared with controlled students,
and participants who engaged in twelve uplift events exhibited lower stress compared with whom engaging two or none uplifts,
implicating the protective effect of uplift events on adolescents.

%3.对自杀，孤独感，压力的调节作用
Positive events are verified as protective factors against loneliness, suicide,
daily stressors, depression and helping improve health.
\citep{Chang2015Loneliness} investigated the protective effect of positive events in a sample of 327 adults, and found that the positive association between loneliness and psychological maladjustment was found to be weaker for those who experienced a high number of positive life events, as opposed to those who experienced a low number of positive life events.
This is assistant with the conclusion made by \citep{Evan2014Social} that positive events act as protective factors against suicide individually and synergistically when they co-occur, by buffering the link between important individual differences risk variables and maladjustment.
Through exploring naturally occurring daily stressors,
\citep{Ong2006Psychological} found that over time,
the experience of positive emotions functions to assist high-resilient individuals to recover effectively from daily stress.
In the survey made by \citep{Santos2013The}, strategies of positive psychology are checked as potentially tools for the prophylaxis and treatment of depression, helping to reduce symptoms and for prevention of relapses.
Through a three-week longitudinal study,
\citep{Bono2013Building} examined the correlation between employee stress and health and positive life events, and concluded that naturally occurring positive events are correlated with decreased stress and improved health.

%4. 青少年积极事件：对身心调节作用
Due to the immature inner status and lack of experience \citep{older},
young people exhibit more exposure to uplift events compared with adults,
such as satisfying social interactions,
excellent academic performance and pleasant entertainments.
Researchers indicate that positive events mitigate the relation between negative events and maladjustment in samples of adolescents experiencing family transitions \citep{Doyle2003Positive}.
The written expression of positive feelings has also be shown to prompt increased cognitive re-organization among an undergraduate student group \citep{Coolidge2009A}.
Positive uplifts can not only help reinforce adolescents' sense of well-being,
help restore the capacity for dealing with stress,
but also have been linked to medical benefits, such as improving mood, serum cortisol levels, and lower levels of inflammation and hyper coagulability \citep{Jain2010Effects}.
Through examining the relationship between self-reported positive life events and blood pressure in 69 sixth graders,
researchers found that increased perceptions of positive life events might act as a buffer to elevated blood pressure in adolescents \citep{Caputo1998Influence}.

%assessment of stress-buffering
To assess the impact of uplift events,
Doyle \emph{et al.} \cite{Kanner1981Comparison} conducted \emph{Hassles and Uplifts Scales},
and concluded that the assessment of daily hassles and uplifts might be a better approach to the prediction of adaptational outcomes than the usual life events approach.
Silva \emph{et al.} \cite{Silva2008The} presented the \emph{Hassles \& Uplifts Scale} to assess the reaction to minor every-day events in order to detect subtle mood swings and predict psychological symptoms.
To measure negative interpretations of positive social events,
Alden \emph{et al.} \cite{Alden2008Social} proposed the interpretation of positive events scale (\emph{IPES}), and analyzed the relationship between social interaction anxiety and the tendency to interpret positive social events in a threat-maintaining manner.
Mcmillen \emph{et al.} \cite{Mcmillen1998The} proposed the \emph{Perceived Benefit Scales} as the new measures of self-reported positive life changes after traumatic stressors, including lifestyle changes, material gain, increases in selfefficacy, family closeness, community closeness, faith in people, compassion, and spirituality.
Specific for college students,
Jun-Sheng \emph{et al.} \cite{Jun2008Influence} investigated in 282 college students using the \emph{Adolescent Self-Rating Life Events Checklist}, and found that the training of positive coping style is of great benefit to improve the mental health of students.
Previous exploration for the protective effect of uplift events on adolescents are mostly conducted in psychological area,
relying on traditional manpower-driven investigation and questionnaire.
In view of the above mentioned literature, this article will be based on the following hypothesize:
\paragraph{\textbf{H}} Positive events could conduct stress-buffering impact on overwhelmed adolescents. 
%H1：规划的积极事件对压力具有缓解作用，使微博压力强度降低，压力持续时间变短
%H2：规划的积极事件对压力具有缓解作用，使青少年微博对压力主题的谈论减少

\subsection{User psychological stress analysis based on social network}
With the high development of social networks,
researches explored applying psychological theories into social network based stress mining,
offering effective tools for adolescent stress sensing.
As billions of adolescents record their life, share multi-media content, and communicate with friends through such platforms, e.g.,
Tencent Microblog, Twitter, Facebook and so on,
researchers tend to digging psychological status from the self-expressed public data source.
Xue \emph{et al.} \cite{Xue2014Detecting} proposed to detect adolescent stress from single microblog utilizing machine learning methods by extracting stressful topic words, abnormal posting time, and interactions with friends.
Lin \emph{et al.} \cite{Lin2014User} construct a deep neural network to combine the high-dimensional picture semantic information into stress detecting.
Based on the stress detecting result,
Li \emph{et al.} \cite{Li2015Predicting}adopted a series of multi-variant time series prediction techniques (i.e., Candlestick Charts, fuzzy Candlestick line and  SVARIMA model) to predict the future stress trend and wave.
Taking the linguistic information into consideration,
Li \emph{et al.} \cite{Li2017Exploring} employed a NARX neural network to predict a teen's future stress level referred to the impact of co-experiencing stressor events of similar companions.
To find the source of teens' stress, previous work \cite{Li2017Analyzing} developed a frame work to extract stressor events from microblogging content and filter out stressful intervals based on teens' stressful posting rate.
%to be add: features [xx][xx][xx]
Given the scholars, we propose to depict the stress-buffering measures in three aspects, and tested the relationships as:

\paragraph{\textbf{H1}} The stress-buffering function of positive events is correlated with
a)posting behavior, b)stress intensity and c)microblog linguistic expressions.

Since previous scholars were conducted in a self-report method,
to utilize the abundant self-exposures in adolescents' microblogs,
the present study propose to work in a non-invasion way.
Therefore, two research questions are proposed:
\paragraph{\textbf{RQ1}} How to (a) automatically sense the positive events experienced by adolescents in a timely manner,
and (b) identify the time interval impacted by a particular positive event.

%to be add [xx]...%与阶段相关的文献
To examine the the dynamic process of stress-buffering,
the present study propose to assess the mitigation effect of positive events
in different phases, and assume that:
\paragraph{\textbf{H2}} positive events cause monotonous stress changes in two cases: a) slowing down the increase in stress at the beginning of stressful events,
and b) promoting the reduction of stress after stressful events.

Given this, the research question to be solved is:
\paragraph{\textbf{RQ2}} How to (a)quantify the impact of positive events on different types of stress,
and (b) identify the temporal order between positive events and monotonous stress changes from microblogs.

In addition,
if the stress-buffering effect of positive events could be automatically assessed,
it helps to predict the future stress changes more accurately.
This will benefit schools and parents in arranging positive events at appropriate times to ease and intervene the psychological stress of students.
Thus we push forward the research from how to find stress to the next stage:
how to deal with stress.
From this perspective, a exploration is conducted at the end of the study:
\paragraph{\textbf{RQ3}} how to predict adolescents' future stress under the mitigation effect of positive events from microblogs?
Specifically, (a)which stress-buffering pattern contributes the most in stress prediction,
and (b)influence of different window lengths on stress prediction accuracy
will be taken into consideration.

\section{Current study}
Given the limitations in the existing literature,
this study proposes a complete solution to verify the stress-buffering effect of positive events on overwhelmed adolescents from social network.
In study 1,
a case study is firstly conducted on the microblog dataset of 124 high school students associated with the school's scheduled positive and stressor event list.
After observing the posting behaviours and contents of stressful teens under the influence of positive events,
several hypothesis are conducted to guide the next step research.
In study 2,
we present the procedure to automatically extract positive events and the corresponding impacted interval from microblogs.
A Chinese linguistic parser model is applied to extract structural positive events from microblogging content,
based on a six-dimensional positive event scale and LIWC lexicons.
In study 3,
to quantify the restoring impact of uplift events,
we describe a teen's stressful behaviours in three groups of measures (stress intensity, posting behaviour, linguistic),
and model the impact of positive events as the statistical difference in comparative situations.
Last but not least,
In study 4,
the present study explores how to predict future stress changes integrating the buffering impact of positive events.
Our exploration provides guidance for school and parents that which kind of positive events could help relieve adolescent' stress in both stress prevention and stress early stopping situations.

%to be add [xx]...%与压力/积极类型相关的文献
%Scholars argued about the major stressors for adolescents,
%and assumed that the stressors are mainly come from school life [xx,xx] and self-cognition [xx,xx].
%Based on microblogging measures proposed in current study,
%we target to examine the following hypotheses:
%\paragraph{\textbf{H3}} positive events conduct the most intensive stress-buffering effects on adolescents' school-life stress.
