\documentclass[5p,times,numbers,authoryear]{elsarticle}

\usepackage{ctex}
\usepackage{lineno}%,hyperref}
\usepackage[colorlinks,citecolor=blue]{hyperref}

\usepackage{graphics}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage{helvet}
\usepackage{courier}
\usepackage{diagbox}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage[justification=centering]{caption}
\usepackage[linesnumbered,ruled,vlined,commentsnumbered]{algorithm2e}
\usepackage{color}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{float}
\usepackage{bm}
\usepackage[normalem]{ulem} % use normalem to protect \emph
\newcommand\hl{\bgroup\markoverwith
  {\textcolor{yellow}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}

\usepackage{hyperref}
\usepackage{breakurl}

\newtheorem{definition}{Definition}
\def\boxend{\hspace*{\fill} $\Box$}
\newcommand{\comment}[1]{}
\renewcommand{\multirowsetup}{\centering}

\journal{Computers in Human Behavior}

\usepackage{appendix}

\begin{document}

\begin{frontmatter}

\title{Stress-Buffering Pattern of Positive Events on Adolescents: \\
An Exploratory Study based on Social Networks}


\begin{abstract}
Stress is viewed as the leading cause of public mental health issues.
Positive events, however, could act as a buffer against stress.
%1.主观自陈 %2.静态视觉
Since stress-buffering effects of positive events in previous studies were mainly examined
by subjective self-reporting,
continuous tracking research at individual behavioral levels still remains to be explored.
In this study,
We collected microblogs (n=27,346) from a high school student group (n=500) to examine the relationship 
between positive events and stress-buffering patterns at both content and behavioral levels. 
%result1 
Through a pilot study we found that stress-buffering patterns of school scheduled positive events (n=75) 
were manifested in both reduction of stress intensity and talking less about academic words on micro-blog.
%result2
Hypothetical tests for stress-buffering effects of positive events 
and monotonous changes of stress intensity under the impact of positive events 
were further conducted based on automatical extracted positive events (n=1,914) from microblogs. 
Stress-buffering effects of positive events 
were closely correlated with posting behaviors (ratio = 80.65\%), 
stress change modes (ratio = 67.74\%) and microblog linguistic expressions (ratio = 74.19\%). 
Positive events conducted most intensive stress-buffering impact on stress from 'family life' (ratio = 83.87\%) dimension, 
followed by 'peer relationships' (ratio = 71.77\%) and 'school life' (ratio = 67.74\%) dimensions. 
%restul3 
Positive events buffered monotonous changes of stress intensity compared with both the front (11.88\% reduction) and rear (5.88\% reduction) adjacent intervals. 
Further, stress-buffering patterns of positive events were incorporated into the prediction of adolescents' future stress. 
This study could inform the use of social network to reach and track the mental status transition of adolescents under stress.
The theoretical and practical implications, limitations of this study and future work were discussed.
\end{abstract}

\begin{keyword}
stress-buffering, positive events, microblogs, adolescents
\end{keyword}
\end{frontmatter}


\input{1introduction}
\input{2literature}
\input{3pilot}
\input{4frame}
\input{5experiment}
\input{6conclude}
\section{Reference}
\bibliographystyle{model4-names}
\bibliography{reference-new}
\end{document}
