\section{Literature review}
\subsection{Stress-buffering function of positive life events.}
%3.对自杀，孤独感，压力的调节作用
Positive events have been verified as protective factors against daily stress~\citep{Ong2006Psychological,Bono2013Building}, loneliness~\citep{Chang2015Loneliness}, suicide~\citep{Evan2014Social}, depression~\citep{Santos2013The}.
The protective effect of positive events was hypothesized to operate in both directly (i.e., more positive events people experienced, the less distress they experience)
and indirectly ways by \emph{'buffering'} the effects of stressors ~\citep{Cohen2010Positive,Shahar2002Positive},
with respect to physiological, psychological, and social coping resources ~\citep{Cohen1984Positive, Needles1990Positive}.
%2.积极事件作用的两种方式
%1.积极事件保护的三个方面
\citep{Folkman1997Positive,Folkman2010Stress} identified three classes of coping mechanisms that are associated with positive events during chronic stress:
positive reappraisal, problem-focused coping, and the creation of positive events.
%4. 青少年积极事件：对身心调节作用
Due to the immature inner status and lack of experience,
adolescents exhibit more sensitive to stressors
(i.e., exams, heavy homework, isolated by classmates, family transitions),
living with frequent, long-term stress~\citep{older}.
Meanwhile, positive events help reinforce adolescents' sense of well-being~\citep{Coolidge2009A},
restore the capacity for dealing with stress~\citep{Doyle2003Positive},
and also have been linked to medical benefits, such as improving mood, serum cortisol levels, and lower levels of inflammation and hyper coagulability \citep{Jain2010Effects,Caputo1998Influence}.
The present study will be based on the consensus conclusions from previous studies that positive events could conduct stress-buffering impact on overwhelmed adolescents.
%20190715 1

\subsection{Assessing stress-buffering function of positive events}
%assessment of stress-buffering
Accurately assessing the process of stress-buffering is important for judging the mental health trends of overwhelmed adolescents.
To assess the stress-buffering effect of positive events,
scholars have proposed much studies based on self-support methods.
Doyle \emph{et al.} \cite{Kanner1981Comparison} conducted \emph{Hassles and Uplifts Scales},
and concluded that the assessment of daily hassles and uplifts might be a better approach to the prediction of adaptational outcomes than the usual life events approach.
Silva \emph{et al.} \cite{Silva2008The} presented the \emph{Hassles \& Uplifts Scale} to assess the reaction to minor every-day events in order to detect subtle mood swings and predict psychological symptoms.
To measure negative interpretations of positive social events,
Alden \emph{et al.} \cite{Alden2008Social} proposed the interpretation of positive events scale (\emph{IPES}), and analyzed the relationship between social interaction anxiety and the tendency to interpret positive social events in a threat-maintaining manner.
Mcmillen \emph{et al.} \cite{Mcmillen1998The} proposed the \emph{Perceived Benefit Scales} as the new measures of self-reported positive life changes after traumatic stressors, including lifestyle changes, material gain, increases in selfefficacy, family closeness, community closeness, faith in people, compassion, and spirituality.
Specific for college students,
Jun-Sheng \emph{et al.} \cite{Jun2008Influence} investigated in 282 college students using the \emph{Adolescent Self-Rating Life Events Checklist}, and found that the training of positive coping style is of great benefit to improve the mental health of students.
However, the above explorations are mostly conducted on self-report investigations,
which might be influenced by social appreciation and pressure from measurement scenarios.
Meanwhile, most scholars focused on single measurement limited by manpower and methods,
while the dynamic process of stress-buffering was difficult to track.

\subsection{Measures and stress analysis based on social network}
As billions of adolescents are recording their life, share multi-media content, and communicate with friends through social networks (e.g., Tencent Microblog, Twitter, Facebook),
researchers explored to apply psychological theories into social network based stress mining from the self-expressed public data source.
Multiple content and user behavioral measures in social networks have been proven effective in user mental state analysis.
Xue \emph{et al.} \cite{Xue2014Detecting} proposed to detect adolescent stress from single microblog utilizing machine learning methods by extracting stressful topic words, abnormal posting time, and interactions with friends.
Lin \emph{et al.} \cite{Lin2014User} construct a deep neural network to combine the high-dimensional picture semantic information into stress detecting.
Based on the stress detecting result,
Li \emph{et al.} \cite{Li2015Predicting}adopted a series of multi-variant time series prediction techniques (i.e., Candlestick Charts, fuzzy Candlestick line and  SVARIMA model) to predict the future stress trend and wave.
Taking the linguistic information into consideration,
Li \emph{et al.} \cite{Li2017Exploring} employed a NARX neural network to predict a teen's future stress level referred to the impact of co-experiencing stressor events of similar companions.
To find the source of teens' stress, previous work \cite{Li2017Analyzing} developed a frame work to extract stressor events from post content and filter out stressful intervals based on teens' stressful posting rate.
Previous scholars focused on stress analysis,
while measures depicting stress-buffering and positive event lack of sufficient verification.
\section{Current study}
Given the limitations in the existing literature,
this study proposes a complete solution to test 
the relationship between stress-buffering characteristics of positive events 
and adolescents' microblogging behaviors in three groups of measures under hypothesis H1,  
and further automatically track the dynamic process of stress-buffering under hypothesis H2: 
\vspace{-0.3 cm}
\paragraph{\textbf{H1}} The stress-buffering function of positive events is correlated with
a)posting behavior, b)stress intensity and c)microblog linguistic expressions.
\vspace{-0.3 cm}
\paragraph{\textbf{H2}} Positive events cause monotonous stress changes in two cases: a) slowing down the increase of stress at the beginning,
and b) promoting the reduction of stress after stressful events.

In response to the theoretical hypothesis, 
we propose new measurement methods in a non-invasion way based on social network data. 
Two research questions are proposed:
\vspace{-0.3 cm}
\paragraph{\textbf{RQ1}}
How to (a) automatically sense the positive events experienced by adolescents in a timely manner,
and (b) identify the time interval impacted by a particular positive event.
\vspace{-0.3 cm}
\paragraph{\textbf{RQ2}}
How to quantify the stress-buffering effect of positive events based on above microblogging characteristics?

To answer above questions, 
a pilot study is firstly conducted on the microblog dataset of 500 high school students associated with the school's scheduled positive and stressor event list.
After observing the posting behaviours and contents of stressed students under the influence of positive events,
several hypothesis are conducted to guide the next step research.
In study 1,
we test the relationship between the stress-buffering effects of automatically extracted positive events and student's microblogging characteristics.
A Chinese linguistic parser model is applied to extract structural positive events from microblogging content based on a six-dimensional positive event scale and LIWC lexicons.
We depict a students's stressful behaviours in three groups of measures (stress intensity, posting behaviour, linguistic),
and model the stress-buffering effect as the statistical difference in two comparative situations.
In study 2,
we track the dynamic process of stress-buffering function,
and quantify the stress-buffering impact of positive events in temporal order.
