%1.共鸣
%This resonated with the study xx suggesting that ...
%This high correlation between positive events and stress-buffering echoes previous studies showing that ... (xx).
%Similarly, scholar also found that students with ...(xx).
%2.意义
% The findings also highlighted the need for .. (xx, xx).
% Therefore, the goals of .. are still salient in stress-buffering on microblogs.

%直接描述findings；按study顺序；这样做有什么创新，好处；其实你想强调的在这里强调就可以。
%In fact, ...;
\section{Discussion and conclusion}
This study gives a deep inside into the stress-buffering function of positive events on adolescents' social networks.
%findings - 对应 Hypothesis
Positive events were validated to alleviate the psychological stress of overwhelmed high school students on microblogs,
in particular academic stress and self-cognitive stress.
%贡献: 从survey -> social-based
This article extended the stress-buffering impact of positive events from traditional survey-based method
to automatically detection method from social network data.
%首次提出
The present study first conduct the comprehensive framework to automatically detect positive events and quantify its stress-buffering effects from the microblogs posted by high school students.
%结果表明
Experimental results show that
our model could measure the restoring impact of school scheduled positive events efficiently,
and integrating the impact of positive events helps reduce the stress prediction errors.
This exploratory work provides guidance for school and parents that
which kind of positive events could help relieve students' overwhelmed stress
in both stress prevention and stress early stopping situations.

There were four groups of results in this work.
The first group of findings relates to the Hypothesis 1, which assumes positive events can conduct stress-buffering effects on adolescents.
In study 1, the scheduled school events with exact time intervals and the microblogs posted by 124 students are collected and statistically analyzed.
Results showed that when positive events are scheduled neighboring stressful events, 
students exhibits less stress intensity and shorter stressful time intervals from their microblogs. 
In response to the stressor event of exam, 
the study found that most students talked less about the upcoming or just-finished exams when positive events happened nearby,
with lower frequency and lower ratio. 
The results substantiated previous studies reporting the protective effect of positive events on adolescents~\citep{Cohen2010Positive,Shahar2002Positive} using laboratory methods. 
Based on this, this article carried out more in-depth follow-up studies. 

The second groups of results are presented in study 2,
displaying the structural results of extracting positive events from adolescents' microblogs. 


The third groups of results in study 3 directly relates to the stress-buffering patterns of positive events.


The fourth groups of results should be considered as exploratory and application.
In study4,
this study integrated the impact of positive events into traditional stress prediction in time line,
and verified whether the restoring patterns of each type of positive events could help improve the prediction performance,
showing the effectiveness of the model in quantifying the impact of positive events,
as well as the easing function of positive events during the process of dealing with stress. 

%最后可以写 microblog-based方法的优势，以及学生并不愿意讲，但是压力状态下会讲更多(xx在原笔记)。因此尽管我们是尝试，但是打开了新渠道。

\section{Limitations and future work}

This study has a number of limitations.
% 1) study 1 的数据观察忽略了个人事件
First, it used the microblog data set collected from the social network of high school students,
and choose the scheduled positive/stressor school events as the ground truth in the case study.
This could be seen as a relative rude verification method,
because individual events (i.e., 'lost love', or 'received a birthday present') may also have an impact,
except for events planned by the school.
Therefore, the data observation in the first study are not 100\% rigorous and need further verification.

% 2) 从侧面证明了stress-buffering
Second, this paper validate the stress-buffering impact of positive events according to the improved stress prediction accuracy indirectly.
At best, it conducts some self-validation in various perspectives of algorithm.
We need to conduct more convincing experiments
through inviting the participants to complete related scales (e.g., uplift and stressor scales),
thus to find the direct verification for such findings.

% 3) 未考虑叠加影响
Finally, this study treats positive events as independent existence and studies the impact of each event separately,
which ignores the additive and collective effects of multiple positive events at the same time.
Thus, our future research may investigate the overlap effects of multiple positive events,
as well as the frequent co-appearing patterns of different types of positive events and stressor events,
thus to provide more accurate stress-buffering and restoring guidance for individual adolescents.

%: 1) personality, 2) social support 
Based on current research implications,
more factors could help analyze the stress restoring patterns among adolescents more comprehensively in future research.
Specifically, one factor is how personality impacts the stress-buffing of positive events \citep{personality1,personality2},
which could be captured from the social media contents \citep{xx}.
Another key factor is the role the social support \citep{socialSupport1, socialSupport2} in social networks plays.
This factor leaves clues in the messages under each post,
and the behaviors (i.e., retweet, the like numbers) of friends. 
%social support
\citep{socialSupport1} showed
number of Facebook friends associated with stronger perceptions of social support,
which in turn associated with reduced stress, and in turn less physical illness and greater well-being.
\citep{socialSupport2} indicated that experiencing important life events can have a long term deleterious impact on subjective well-being, which could be partially abated by receiving social support from Facebook friends.
The corresponding experimental design, and the online-offline complementary verification methods will be the key challenges in the future work.

%后续结合线上线下会更准确。但是大数据量下难以执行，有效的自动标记方法需要更多的探索。
