\section{Literature review}
\subsection{Stress-buffering function of positive life events}
%3.对自杀，孤独感，压力的调节作用
Positive events have been verified as protective factors against daily stress~\citep{Ong2006Psychological,Bono2013Building}, loneliness~\citep{Chang2015Loneliness}, suicide~\citep{Evan2014Social} and depression~\citep{Santos2013The}.
The protective effect of positive events was hypothesized to operate in both directly (i.e., the more positive events people experienced, the less stress they perceived)
and indirectly ways by \emph{'buffering'} the effect of stressors ~\citep{Cohen2010Positive,Shahar2002Positive},
with respect to physiological, psychological, and social coping resources ~\citep{Cohen1984Positive, Needles1990Positive}.
%2.积极事件作用的两种方式
%1.积极事件保护的三个方面
%\citep{Folkman1997Positive,Folkman2010Stress} identified three classes of coping mechanisms that are associated with positive events during chronic stress:
%positive reappraisal, problem-focused coping, and the creation of positive events.

%4. 青少年积极事件：对身心调节作用
Due to the immature inner status and lack of experience,
adolescents exhibit more sensitive to stressors
(i.e., exams, heavy homework, isolated by classmates, family transitions),
living with frequent, long-term stress~\citep{older}.
In this situation,
positive events could help reinforce adolescents' sense of well-being~\citep{Coolidge2009A},
restore the capacity for dealing with stress~\citep{Doyle2003Positive},
and also have been linked to medical benefits, such as improving mood, serum cortisol levels, and lower levels of inflammation and hyper coagulability \citep{Jain2010Effects,Caputo1998Influence}.
The present study will be based on the consensus conclusions from the above studies
that positive events could conduct stress-buffering effect on stressed adolescents.
%20190715 1

\subsection{Assessing the stress-buffering effect of positive events}
To assess the stress-buffering effect of positive events,
scholars have conducted many studies based on self-support methods,
including Hassles and Uplifts Scales~\citep{Kanner1981Comparison},
Interpretation of Positive Events Scale~\citep{Alden2008Social},
Perceived Benefit Scales~\citep{Mcmillen1998The},
Adolescent Self-Rating Life Events Checklist~\citep{Jun2008Influence}.
For example,
\citep{Mcmillen1998The} proposed the Perceived Benefit Scales as a new measure of self-reported positive life changes after traumatic stressors (i.e., lifestyle changes, family closeness, community closeness).
\citep{Jun2008Influence} investigated 282 college students using the Adolescent Self-Rating Life Events Checklist,
and found that the training of positive coping style is of great benefit to improve the mental health of students.
While, the above explorations based on self-report investigations
are difficult to exclude interference from external factors (i.e., social appreciation, pressure from measurement scenarios).
Meanwhile, due to the lack of manpower and effective scientific methods,
most scholars relies on a limited number of measurements,
thus continuous measurements of stress-buffering process was difficult to carry out.

\subsection{Measures and stress analysis based on social network}
As billions of adolescents are recording their life through social networks (e.g., micro-blog, Twitter, Facebook),
researchers explored to apply psychological theories into social network based data mining techniques.
Multiple content and user behavioral measures have been proven effective in user mental health analysis,
including time series curve analysis of stress~\citep{Li2015When,Li2015Using}, topic words~\citep{XueUbicomp13}, abnormal posting time~\citep{Xue2014Detecting},
online shopping behaviors~\citep{DBLP:conf/apweb/Zhao0XLF16},
human mobility features~\citep{DBLP:conf/dasfaa/JinXLF16}, comment/response actions~\citep{Liang2015Teenagers},
high dimensional multimedia features~\citep{Lin2014User}.
For example, \citep{Xue2014Detecting} proposed to detect adolescent stress from microblogs utilizing machine learning methods by extracting stress topic words and abnormal posting time.
\citep{Li2017Analyzing} proposed to detect stressor events from microblog content
and analyze stressful intervals based on posting rate.
The above studies focus on the discussion of stress detection on social networks,
while the pattern of stress-buffering and the role of positive events in stress coping process is still insufficiently discussed.

\subsection{Current study}
Given the limitations in the existing literature,
this study examined the relationship between positive events and stress-buffering pattern
based on adolescents' microblog content and behaviors.
Two hypotheses were tested:
%%\vspace{-0.3 cm}
%\begin{itemize}[leftmargin=*]
% \item[1.] The stress-buffering effect of positive events is correlated with
%a)posting behavior, b)stress change mode and c)microblog linguistic expressions.
%\item[2.] Positive events buffers monotonous stress changes at both the early stage (before stress beginning)
%and late stage (after the end of stress).
%\end{itemize}
%\vspace{-0.3 cm}
\paragraph{\textbf{H1}} The stress-buffering effect of positive events is correlated with
a)posting behavior, b)stress change mode and c)microblog linguistic expressions.
\vspace{-0.3 cm}
\paragraph{\textbf{H2}} Positive events buffers monotonous stress changes at both the early stage (before stress beginning)
and late stage (after the end of stress).

In response to the theoretical hypothesis,
we propose new measurement methods in a non-invasion way based on public social network data.
Two research questions are proposed: 
%\begin{itemize}[leftmargin=*]
%\item[1.] How to (a) automatically extract the positive events experienced by adolescents from microblogs,
%and (b) identify the time interval impacted by a particular positive event.
%\item [2.] How to quantify the stress-buffering effect of positive events based on above microblog characteristics?
%\end{itemize}
%
\vspace{-0.3 cm}
\paragraph{\textbf{RQ1}}
How to (a) automatically extract the positive events experienced by adolescents from microblogs,
and (b) identify the time interval impacted by a particular positive event.
\vspace{-0.3 cm}
\paragraph{\textbf{RQ2}}
How to quantify the stress-buffering effect of positive events based on above microblog characteristics.

To answer above questions,
a pilot study was firstly conducted on the microblog data set (n=29,232) of a group of high school students (n=500) 
associated with the school's scheduled positive events (n=259) and stressor events (n=518). 
After observing the posting behaviors and contents of stressed students under the influence of positive events, 
several implications were discussed to guide the next step research.
In study 2,
we examined the relationship between the stress-buffering pattern 
of automatically extracted positive events and adolescents' microblog characteristics. 
A Chinese linguistic parser model was applied to extract structural positive events.
We depicted an adolescent's stressful behaviors in three groups of measures 
(posting behaviour, stress change mode, linguistic expressions), 
and modeled the stress-buffering effect as the statistical difference in two comparative situations. 
In study 3, 
we tracked the dynamic process of stress-buffering pattern,
and quantify the monotonous stress-buffering impact in temporal order. 